---
title: "PPSN Meeting, Fall 2023"
subtitle: "Update on yield data processing"
author: "Samuel Robinson, Ph.D."
date: "Oct 18, 2023"
output: 
  beamer_presentation:
    incremental: false
    theme: "default"
    colortheme: "lily"
    highlight: "tango"
urlcolor: blue
df_print: kable
classoption: aspectratio=169   
header-includes: 
  - \useinnertheme{circles}
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, message=TRUE, 
                      warning=TRUE, cache = TRUE, fig.height=5,fig.width=5)

library(tidyverse)
library(sf)
library(stars)
library(ggpubr)
theme_set(theme_classic())

source("C:\\Users\\Samuel\\Documents\\Projects\\UofC postdoc\\PPSN_code\\helperFunctions.R")
load("C:\\Users\\Samuel\\Dropbox\\PPSN Cleaned Yield\\Rasterized yield\\canProf.Rdata")

ha2ac <- 2.47105

canProf <- canProf[sapply(canProf,class)=='data.frame'] %>% 
  bind_rows(.id='Grower') %>% 
  filter(Yield_buAc!=0,!is.na(Yield_buAc))

# canProf <- canProf %>% 
#   mutate(CropType=gsub('Winter ','W.',CropType),
#          CropType=gsub('Spring ','S.',CropType))

#Provinces outlines
canProvPath <- "C:\\Users\\Samuel\\Documents\\Shapefiles\\Canada provincial\\gpr_000b11a_e.shp"


canProvinces <- read_sf(canProvPath) %>% 
  filter(grepl("(Alberta|Saskatchewan)",PRENAME)) %>% 
  st_transform(3978)

bPolyPath <- "C:\\Users\\Samuel\\Dropbox\\PPSN Cleaned Yield\\Field Boundaries"
sFiles <- dir(bPolyPath,"*.shp",full.names = TRUE)

#Centroids for each field, plus polygon area
fieldCent <- lapply(sFiles,function(x){
  read_sf(x) %>% 
    transmute(Field=Field,area_m2=as.numeric(st_area(.))) %>%
    st_centroid() %>% st_transform(3978)
}) %>% setNames(nm=gsub('_poly.shp','',dir(bPolyPath,"*.shp"),fixed=TRUE)) %>% 
  bind_rows(.id='Grower')


```

## Update on yield data collection

::: columns

:::: column 

- `r length(unique(canProf$Grower))` growers' datasets loaded

- 4 datasets in progress: require custom coding for each dataset

- `r canProf %>% mutate(GrowerFieldYear=paste0(Grower,'_',FieldYear)) %>% pull(GrowerFieldYear) %>% unique() %>% length` field-years, `r canProf %>% transmute(FieldYear=paste0(Grower,'_',gsub('_[0-9]{4}$','',FieldYear))) %>% unique() %>% nrow()` individual fields

- `r canProf %>% select(Grower,FieldYear) %>% distinct() %>% separate(FieldYear,c('Field','Year'),sep='_') %>% pull(Year) %>%  unique() %>% length` years of data (`r canProf %>% select(Grower,FieldYear) %>% distinct() %>% separate(FieldYear,c('Field','Year'),sep='_') %>% pull(Year) %>% range() %>% paste0(.,collapse='-')`)

- `r canProf %>% pull(CropType) %>% unique() %>% length` crop types

- Field areas (acres): 
  - Total = `r as.character(round(sum(ha2ac*fieldCent$area_m2/10000)))`
  - Mean = `r round(mean(ha2ac*fieldCent$area_m2/10000),1)`
  - Median = `r round(median(ha2ac*fieldCent$area_m2/10000),1)`
  - Min = `r round(min(ha2ac*fieldCent$area_m2/10000),1)`
  - Max = `r round(max(ha2ac*fieldCent$area_m2/10000),1)`

::::

:::: column

```{r fieldLocs}
ggplot()+
  geom_sf(data=canProvinces,fill='white')+
  geom_sf(data=fieldCent,size=0.2)
```

::::

:::

## Acreage by year

```{r yearYield, fig.width=8, fig.height=4}
canProf %>% count(FieldYear) %>% ungroup() %>% mutate(n=n*0.0988421526) %>% 
  separate(FieldYear,c('Field','Year'),sep='_') %>% 
  mutate(Year=factor(Year,levels=2012:2022)) %>%
  group_by(Year,.drop = FALSE) %>% 
  summarize(ac=sum(n)) %>% 
  ggplot(aes(x=Year,y=ac))+geom_col()+labs(x='Year',y='Total acres')
```

## Overall yield

```{r overallYield, fig.width=8, fig.height=4}
canProf %>% filter(Yield_buAc<250) %>%  
  ggplot(aes(x=Yield_buAc,y=after_stat(count),weight=0.0988421526))+
  geom_histogram(binwidth = 5)+
  labs(x='Yield (bu/ac)',y='Acres')
```

## Crop specific yield

```{r cropYield, fig.width=8, fig.height=4}
canProf %>% 
  filter(CropType!='Chickpeas') %>% 
  # slice_sample(n=20000) %>%
  group_by(CropType) %>% 
  mutate(n=n()*0.0988421526) %>% 
  filter(Yield_buAc<quantile(Yield_buAc,0.99)) %>% 
  mutate(nFields=length(unique(FieldYear))) %>% 
  ungroup() %>% 
  mutate(CropType=paste0(CropType,'\n',round(n),' ac, ',nFields,' fields')) %>% 
  arrange(desc(n)) %>% 
  filter(CropType %in% unique(CropType)[1:12]) %>% 
  mutate(CropType=factor(CropType,levels=unique(CropType))) %>% 
  ggplot(aes(x=Yield_buAc,y=after_stat(count),weight=0.0988421526))+
  geom_histogram(bins=30)+
  facet_wrap(~CropType,scales='free',ncol=4,nrow=3)+
  labs(x='Yield (bu/ac)',y='Acres')

```
Not shown: corn, chickpeas, soybeans

## Overall profit (2022 only)

```{r overallProf, fig.width=8, fig.height=4, warning=FALSE}

canProf %>% 
  ggplot(aes(x=Profit_ac,y=after_stat(count),weight=0.0988421526))+
  geom_histogram(breaks=seq(-200,2000,20),aes(fill=Profit_ac<0),show.legend = FALSE)+
  annotate(geom='text',x=0,y=10000,label=
             paste0(round(100*mean(canProf$Profit_ac<0,na.rm=TRUE),2),'%\nunprofitable'),
           col='red') +
  labs(x='Profit ($/ac)',y='Acres')+
  coord_cartesian(xlim=c(NA,2000))+
  scale_fill_manual(values=c('grey30','red'))

```

## Crop-by-crop profit (2022 only)

```{r cropProf, fig.width=8, fig.height=4, warning=FALSE, message=FALSE}
canProf %>%  filter(!is.na(Profit_ac)) %>% 
  # slice_sample(n=20000) %>%
  filter(CropType!='Chickpeas') %>% 
  group_by(CropType) %>% 
  mutate(n=n()*0.0988421526) %>% 
  filter(Yield_buAc<quantile(Yield_buAc,0.99)) %>% 
  mutate(nFields=length(unique(FieldYear))) %>% 
  ungroup() %>% 
  mutate(CropType=paste0(CropType,'\n',round(n),' ac, ',nFields,' fields')) %>% 
  arrange(desc(n)) %>% 
  mutate(CropType=factor(CropType,levels=unique(CropType))) %>% 
  ggplot(aes(x=Profit_ac,y=after_stat(count),weight=0.0988421526))+
  geom_histogram(aes(fill=Profit_ac<0),show.legend = FALSE)+
  facet_wrap(~CropType,scales='free')+
  labs(x='Yield (bu/ac)',y='Acres')+
  scale_fill_manual(values=c('grey30','red'))
```

## Challenge: missing data or zero yield?

```{r fieldNAmap, fig.width=8,fig.height=4}
load("C:\\Users\\Samuel\\Documents\\Projects\\UofC postdoc\\PPSN_code\\carpFigures2023\\yieldHistDat.RData")

#Cells inside field
inField <- st_intersects(rast,fBound,sparse = FALSE,as_points = TRUE)

rast <- rast %>% #Changes NA cells within field to 0.01
  mutate(Yield_tha=ifelse(is.na(Yield_tha)&inField,0.01,Yield_tha)) %>%
  mutate(Profit_ha=Yield_tha*priceDat$CropPrice_t-priceDat$AvgCost_ha) %>% 
  mutate(Profit_ha_cat=cut(Profit_ha,breaks = c(min(Profit_ha,na.rm = TRUE),0,400,800,max(Profit_ha,na.rm=TRUE)),include.lowest=TRUE,
                           labels=c('<$0','$0-400','$400-800','>$800'))) %>% 
  mutate(Profit_ha_cat=factor(Profit_ha_cat,levels=rev(levels(Profit_ha_cat)))) %>% 
  mutate(Profit_ac=Profit_ha/2.47105) %>% 
  mutate(Profit_ac_cat=cut(Profit_ac,breaks = c(min(Profit_ac,na.rm = TRUE),0,100,200,300,400,max(Profit_ac,na.rm=TRUE)),include.lowest=TRUE,
                           labels=c('<$0','$0-100','$100-200','$200-300','$300-400','>$400'))) %>% 
  mutate(Profit_ac_cat=factor(Profit_ac_cat,levels=rev(levels(Profit_ac_cat))))

#Transform
epsgCode <- 2957 #Sask UTM 13
# epsgCode <- 3401 #AB 10 
fBound <- fBound %>% st_transform(epsgCode)
rast <- rast %>% st_transform(epsgCode)
badSpots <- badSpots %>% st_transform(epsgCode)

#Categorized plot
rastNA <- rast %>% 
  mutate(Profit_ac_cat=ifelse(Yield_tha==0.01,NA,Profit_ac_cat)) %>% 
  mutate(Profit_ac_cat=factor(Profit_ac_cat,labels=levels(rast$Profit_ac_cat)))

p1 <- ggplot()+
  geom_stars(data=rastNA,aes(fill=Profit_ac_cat),na.action = na.omit)+
  scale_fill_viridis_d(option='E',na.value = NA,direction = -1)+ #Cividis colour scheme
  theme_bw()+labs(x=NULL,y=NULL,fill='Dollars\nper acre')+
  theme(axis.text = element_blank(),axis.ticks = element_blank(),
        panel.grid = element_blank(),legend.position = 'right')

p2 <- ggplot()+
  geom_stars(data=rast,aes(fill=Profit_ac_cat),na.action = na.omit)+
  scale_fill_viridis_d(option='E',na.value = NA,direction = -1)+ #Cividis colour scheme
  theme_bw()+labs(x=NULL,y=NULL,fill='Dollars\nper acre')+
  theme(axis.text = element_blank(),axis.ticks = element_blank(),
        panel.grid = element_blank(),legend.position = 'right')

ggarrange(p1,p2,ncol=2,common.legend = TRUE, legend='right')

```

## Challenge: missing data or zero yield (cont.)

```{r fieldNAfig, fig.width=8, fig.height=4}

yieldHistDat <- data.frame(prof=as.vector(rast$Profit_ac),profCat=as.vector(rast$Profit_ac_cat),
                           fillin=as.vector(rast$Yield_tha)==0.01,
                           badSpot=factor(sapply(st_intersects(rast,badSpots,sparse = TRUE),function(x) if(length(x)==0) 0 else x))) %>%
  filter(!is.na(prof)) %>% 
  mutate(prof=ifelse(prof>-90,prof,-50)) %>%
  mutate(profCat=factor(profCat,levels=levels(rast$Profit_ac_cat)))

#Compare profit distributions
p1 <- yieldHistDat %>% filter(!fillin) %>% 
  ggplot()+
  geom_histogram(aes(x=prof,y=after_stat(count),weight=0.0988421526,fill=prof<0),
                 breaks=seq(-100,856,20),show.legend = FALSE)+
  labs(x='Profit ($/acre)',y='Number of acres')+
  geom_text(x=400,y=20,aes(label=paste0(round(100*mean(prof<0),2),'% Unprofitable')),col='red')+
  theme_classic()+
  scale_fill_manual(values=c('grey30','red'))

p2 <- yieldHistDat %>% ggplot()+
  geom_histogram(aes(x=prof,y=after_stat(count),weight=0.0988421526,fill=prof<0),
                 breaks=seq(-100,856,20),show.legend = FALSE)+
  labs(x='Profit ($/acre)',y='Number of acres')+
  geom_text(x=400,y=40,aes(label=paste0(round(100*mean(prof<0),2),'% Unprofitable')),col='red')+
  theme_classic()+
  scale_fill_manual(values=c('grey30','red'))

ggarrange(p1,p2,ncol=1)

```

## Data coverage (per field)

```{r dataCoverage, fig.width=8, fig.height=4, warning=FALSE, message=FALSE}

bPolyPath <- "C:\\Users\\Samuel\\Dropbox\\PPSN Cleaned Yield\\Field Boundaries"
sFiles <- dir(bPolyPath,"*.shp",full.names = TRUE)

fieldAreas <- lapply(sFiles,function(x){
  read_sf(x) %>% 
    transmute(Field=Field,area_m2=as.numeric(st_area(.))) %>% 
    st_drop_geometry()  
}) %>% setNames(nm=gsub('_poly.shp','',dir(bPolyPath,"*.shp"),fixed=TRUE)) %>% 
  bind_rows(.id='Grower')

rastCoverage <- canProf %>% 
  filter(!is.na(Yield_buAc)) %>% 
  count(Grower,FieldYear) %>% 
  ungroup() %>% 
  separate(FieldYear,c('Field','Year'),sep='_') %>% 
  left_join(fieldAreas,by=c('Grower'='Grower','Field'='Field')) %>% 
  mutate(prop=n*(20^2)/area_m2)

rastCoverage %>% filter(prop<1.1) %>% 
  ggplot(aes(x=prop))+geom_histogram()+
  geom_vline(xintercept = 1,col='black')+
  geom_vline(xintercept=c(0.74,0.93,1),linetype='dashed',col='red')+
  annotate('text',x=c(0.74,0.93,1)-0.04,y=1300,label=c('25th','50th','75th'),size=3,col='red')+
  labs(x='Proportion raster coverage',y='Number of fields')+
  scale_x_continuous(breaks=seq(0,1,0.25))

```

## Other challenges

- Grower records
  - Need standardization/name matching
  - Mismatches between yield data, grower records, satellite data
- Data Filtering 
  - Parameters (i.e. "throw out when X = ...")
  - Order of filtering pipeline
  - Combine back-correction smoothing
  - Not trivial: affects grower reports, final models, and grower trust/buy-in
  - __GARBAGE IN, GARBAGE OUT__
- Further profit mapping
  - Require economic data prior to 2022

