---
title: "PPSN Grower Report"
geometry: margin=2cm
fontsize: 12pt
output: 
  pdf_document: 
    toc: false
params:
  GROWERNAME: "gname"
  NUMFIELDYEARS: "nfy" 
  NUMCROPS: "nc"
  NUMYEARS: "ny"
  PERCMARGACRES: "pmac"
  TABLEHERE: "tabhere"
  FIGUREHERE: "fighere"
header-includes:
  - \usepackage{multicol}
  # - \usepackage{caption}
  # - \captionsetup[table]{labelformat=empty}
# output: 
#   bookdown::pdf_document2:
#     toc: false
#     fig_caption: yes
#     keep_tex: false

---

```{r setup, include=FALSE}
library(knitr)
# library(kableExtra)
library(dplyr); library(tidyr); library(ggplot2)

knitr::opts_chunk$set(echo = FALSE)

```

\begin{multicols}{2}

Thank you `r params$GROWERNAME` for your contribution. This page has been prepared exclusively for you and has not been shared publicly.

You supplied the project with:
\begin{itemize}
  \item `r params$NUMFIELDYEARS` field years of data
  \item `r params$NUMCROPS` different crop types
  \item `r params$NUMYEARS` years of data
\end{itemize}

Quick Facts about your data:
\begin{itemize}
  \item In 2022 `r params$PERCMARGACRES`\% of total acres were marginal (less than \$0 profit/acre)
\end{itemize}

\columnbreak

\textbf{Average yield in bu\/ac for each crop}

```{r yieldTab}

params$TABLEHERE #%>% kable()

```

\textbf{Do these numbers look accurate? Let us know}

\end{multicols}

```{r profFigure, fig.height=4, fig.width=7.5}
  
  # print('FIGUREHERE')
  params$FIGUREHERE

```

Thank you again for your support. We look forward to connecting with you when data collection resumes in the fall. Have a great summer!
