---
documentclass: article
geometry: margin=1cm,top=3.5cm,headheight=3.5cm,headsep=0cm
fontsize: 12pt
output: 
  pdf_document: 
    latex_engine: xelatex
    toc: false
    keep_tex: false
    includes:
      in_header: headIncl.tex
params:
  GROWERID: "gid"
  NUMFIELDYEARS: "nfy" 
  NUMCROPS: "nc"
  NUMYEARS: "ny"
  PERCMARGACRES: "pmac"
  TABLEHERE: "tabhere"
  FIGUREHERE: "fighere"
title: ""

---

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)

knitr::opts_chunk$set(echo = FALSE)

```


<!-- Need to add a banner here, and possibly some logos. Some possible links that might help: -->
<!-- https://tex.stackexchange.com/questions/297240/adding-an-image-to-a-header-in-latex -->
<!-- https://bookdown.org/yihui/rmarkdown-cookbook/latex-logo.html -->
<!-- https://tex.stackexchange.com/questions/276358/text-on-background-image-footer-and-header/276453 -->
<!-- https://tex.stackexchange.com/questions/411212/set-header-background-and-text-color-using-fancyhdr -->

<!-- Eventual goals: -->
<!-- https://rfortherestofus.com/2021/11/multicolumn/ -->

<!-- Begin multiple columns. For columns of different widths, might need vwcol or flowfram: https://tex.stackexchange.com/questions/89721/different-column-widths-using-multicol -->

<!-- \begin{center} -->
<!--   \makebox[\textwidth]{\includegraphics[width=\paperwidth]{PPSNnewsletter_Jul4.pdf}} -->
<!-- \end{center} -->
<!-- \noindent -->
<!-- \includegraphics[width=\paperwidth]{./PPSNnewsletter_Jul4.pdf} -->
\includepdf[pages=-]{PPSNnewsletter_Aug24.pdf}
\pagebreak

\begin{tikzpicture}[remember picture,overlay]
<!-- Upper teal banner -->
 	\fill[ppsnTeal] (current page.north west) rectangle ([yshift=0cm] current page text area.north  -| current page.east);
<!-- Lower teal banner -->
 	\fill[ppsnTeal] (current page.south west) rectangle ([yshift=0.9cm] current page text area.south -| current page.east);
<!-- PPSN logo -->
 	\node[anchor=north west,rectangle,,yshift=-0.5cm,xshift=0.5cm] at (current page.north west){\includegraphics[height=2.3cm]{ppsnLogo.png}};
<!-- Upper text -->
 	\node[draw=black,minimum height = 2.3cm,minimum width=8cm,anchor=north east,font=\color{white}\LARGE\linespread{1}\selectfont, fill=ppsnBlue,rectangle,yshift=-0.5cm,xshift=-0.5cm,align=right] at (current page.north east){
  Grower Edition:\\ Summer 2023 Update
 	}
 	;
<!-- USask logo -->
 	\node[anchor=south west,rectangle,xshift=0.5cm,yshift=0.25cm] at (current page.south west){\includegraphics[height=1.05cm]{uSaskLogo.png}};
<!-- UCalgary logo -->
 	\node[anchor=south east,rectangle,xshift=-0.6cm,yshift=0.25cm] at (current page.south east){\includegraphics[height=1.1cm]{uCalgaryLogo.png}};
 \end{tikzpicture}
 
<!-- \fancyhead[R]{ -->
<!--   \begin{tcolorbox}[colback=ppsnBlue,halign=right,width=8cm] -->
<!--   \LARGE -->
<!--   \color{white} -->
<!--   Grower Edition:\\Summer 2023 Update -->
<!--   \end{tcolorbox} -->
<!-- } -->


\color{ppsnBlue}
\setstretch{0.9}	
\LARGE
\textbf{PPSN Preliminary Report: Grower ID `r params$GROWERID`}

\normalsize
\setstretch{1}
\color{black}

\begin{multicols}{2}

Thank you for your contribution to this project! This page has been prepared exclusively for you and has not been shared publicly.

You supplied the project with:
\begin{itemize}
  \item `r params$NUMFIELDYEARS` field years of data
  \item `r params$NUMCROPS` different crop types
  \item `r params$NUMYEARS` years of data
\end{itemize}


```{r percMarg, eval = !is.na(params$PERCMARGACRES), echo=FALSE, results='asis'} 
cat("Quick facts about your data")
cat("\\begin{itemize}")
cat(paste0("\\item In 2022, ",params$PERCMARGACRES,"\\% of total acres were marginal (less than \\$0 profit/acre)."))
cat("\\end{itemize}")
```


\columnbreak

\vspace*{0.5cm}

\begin{centering}

\textbf{Average yield for each crop type (bushels/acre)}

```{r yieldTab}

smallCols <- which(nchar(colnames(params$TABLEHERE))>9)
if(length(smallCols)==0) smallCols <- 0

params$TABLEHERE %>% 
  kable(format = 'latex') %>% 
  column_spec(column=smallCols,width='1.2cm')

```

\textbf{Do these numbers look accurate? Let us know}

\end{centering}


\end{multicols}

```{r profFigure, fig.height=4, fig.width=7.5}
  
  # print('FIGUREHERE')
  params$FIGUREHERE

```

\begin{tcolorbox}[colback=ppsnBlue,arc=0mm,halign=flush center,frame empty]
  \color{white}
  \large
  Thank you again for your support. We look forward to connecting with you when data collection resumes in the fall. Have a great harvest!
\end{tcolorbox}


```{r endCleanup}
detach("package:kableExtra", unload = TRUE)
```
